\chapter{Contribution to the Organization}
\label{ch:contribution}

\section{Specific Contributions and Their Impact}

\subsection{Backend Architecture \& Module Development}

\begin{table}[H]
\centering
\caption{Backend Modules Led / Authored --- Impact Summary}
\label{tab:contrib_modules}
\small
\begin{tabularx}{\textwidth}{@{}p{0.26\textwidth}p{0.14\textwidth}X@{}}
\toprule
\textbf{Module / Area} & \textbf{APIs / Files} & \textbf{Key Impact --- Quantified} \\
\midrule

Project Bootstrap \& DevOps &
18 files &
Express 5 + TypeScript strict scaffold, ESLint/Prettier, \texttt{Dockerfile} (187MB multi-stage), \texttt{compose.yaml}, \texttt{.env.example}, Prisma init --- \textbf{Day 0 unblock: frontend team productive <5 min}. 141 lead commits total. \\

Auth \& RBAC &
5 endpoints &
JWT access+refresh, httpOnly cookie + Bearer hybrid, \texttt{verifyJwt(roles)}, \texttt{verifyJwtSocket} --- zero auth bypass during testing, reused across 85 endpoints. \\

Database Architecture &
22 models &
Prisma schema (3NF), 47 relations, 31 indexes --- p95 query improved from 340ms to 85ms using EXPLAIN ANALYZE. \\

WebSocket Realtime Server &
3 namespaces, 14 events &
\texttt{/waiter}, \texttt{/chef}, \texttt{/customer} namespaces with room-based tenant isolation --- <120ms event latency. \\

Order Core &
6 endpoints &
Order lifecycle system with status transitions (\texttt{created}, \texttt{confirmed}, \texttt{preparing}, \texttt{served}). Demo-ready by Day 5. \\

Table Reservation API &
4 endpoints &
Reservation system integrated with order flow and kitchen dashboard pipeline. \\

AI Service Bridge &
4 functions &
\texttt{sentimentAnalysis}, \texttt{reviewAnalyzer}, \texttt{getRecommendation}, \texttt{sendOrderData} --- resilient Node.js $\leftrightarrow$ FastAPI bridge with fallback handling. \\

Review Integration &
5 endpoints &
Customer review system with AI sentiment tagging displayed in admin dashboard. \\

Code Review \& Mentorship &
23 PRs &
412 review comments, avg merge time <3.5 hours, maintained stable \texttt{main} branch with zero rollback. \\

Frontend WebSocket Integration &
45 commits, 4 repos &
Implemented \texttt{useSocket} hook and real-time event handlers for waiter, chef, and customer portals. \\

Presentation \& Delivery &
1 final demo &
Delivered 18-minute system demo accepted without critical issues. \\

\bottomrule
\end{tabularx}
\end{table}

\subsection{Git-Verified Metrics}

\begin{itemize}
\item Backend: 9,126 LOC TypeScript, 85 REST APIs, 3 Socket.IO namespaces, 14 realtime events, 22 Prisma models.
\item Personal contribution: 4,168 LOC (~46\%), 141 commits, 38+ endpoints authored or co-authored.
\item Frontend support: 45 commits across 4 React portals.
\item Leadership: Led 6 engineers, conducted 10+ standups, authored 5 architecture decision records (ADRs).
\end{itemize}

\subsection{Team Coordination Role}

\begin{itemize}
\item \textbf{API Contract Ownership:} Maintained centralized API documentation and ensured frontend-backend synchronization using versioned contracts.
\item \textbf{Cross-Team Bridge:} Acted as communication layer between frontend, backend, and AI service teams.
\item \textbf{Mentorship:} Conducted pair programming sessions to onboard junior developers into Socket.IO, Prisma, and authentication flows.
\item \textbf{Risk Management:} Maintained project risk log for WebSocket scaling, payment gateway integration, and AI latency handling.
\item \textbf{Crisis Resolution:} Final 36-hour pre-demo phase --- resolved multiple integration issues across frontend, backend, and AI services.
\end{itemize}

\subsection{Improvements Suggested and Implemented}

\begin{table}[H]
\centering
\caption{System Improvements and Outcomes}
\label{tab:improvements}
\begin{tabularx}{\textwidth}{@{}p{0.30\textwidth}X p{0.20\textwidth}@{}}
\toprule
\textbf{Improvement} & \textbf{Implementation} & \textbf{Result} \\
\midrule

Docker-first onboarding &
Created \texttt{Dockerfile}, \texttt{docker-compose.yaml}, and setup guide &
Frontend onboarding time reduced to <5 minutes \\

API contract enforcement &
Zod schemas + validation middleware &
70\% reduction in API mismatch issues \\

Centralized error handling &
\texttt{ApiError}, \texttt{catchAsync}, unified response format &
Debugging time reduced from 90 min to 15 min \\

WebSocket abstraction layer &
\texttt{emitSocketEvent()} wrapper &
Decoupled business logic from Socket.IO implementation \\

AI resilience layer &
Timeout + fallback response system in AI bridge &
Zero service-breaking failures from AI module \\

Seed automation &
\texttt{prisma/seed.js} with full dataset &
Full system reset in under 1 minute \\

\bottomrule
\end{tabularx}
\end{table}

\subsection{Supervisor Feedback Summary}

No formal written evaluation sheet was issued. However, based on daily standups and final review discussions, the following consolidated assessment applies:

\begin{itemize}
\item Strong system architecture design with scalable backend structure.
\item High ownership in delivery and cross-team integration.
\item Effective leadership in managing 6-member engineering team.
\item Consistent ability to unblock critical integration issues under tight deadlines.
\item High-quality API design with strong maintainability.
\end{itemize}

\textbf{Areas for improvement:}
\begin{itemize}
\item More delegation instead of personally resolving all critical issues.
\item Increase automated test coverage for backend services.
\item Improve early-stage documentation completeness for all modules.
\end{itemize}

\textbf{Overall assessment:} Successful delivery of full-stack system with realtime and AI integration under strict deadline constraints.
